Calculating Entropies With Nested Sampling

### 2017-02-08 paper/ms.tex
New priors

\subsection{The relevance of data}

The degree to which the question ``what is the value of $\x$?'' is
answered by the question ``what is the value of $\d$?'' is given by the
conditional entropy
\begin{align}
H_{\x | \d} &= - \sum_{\d} p(\d) \sum_{\x} p(\x | \d) \log p(\x | \d)
\end{align}
which is the expected value of the entropy of the posterior, averaged over
all possible datasets which might be observed.
This is difficult to compute because the expression
for the posterior distribution
\begin{align}
p(\x | \d) &= \frac{p(\x)p(\d | \x)}{p(\d)}
\end{align}
contains the marginal likelihood $p(\d)$.

@@

The priors are
\begin{align}
A           &\sim \textnormal{Exponential}(1)  \\
\log_{10} T &\sim \textnormal{Uniform}(-1, 0)  \\
\phi        &\sim \textnormal{Uniform}(0, 2\pi)
\end{align}
$A$ and $\phi$ are nuisance parameters. Let $\x = \log_{10} T$.
The prior standard deviation of the noise, $\sigma$, was set to 0.1.
These results were computed using a tolerance of 0.001 for every quantity.
Results:

>>>>

\subsection{The relevance of data}
The degree to which the question ``what is the value of $\x$?'' is
answered by the question ``what is the value of $\d$?'' is given by the
conditional entropy
\begin{align}
H_{\x | \d} &= - \sum_{\d} p(\d) \sum_{\x} p(\x | \d) \log p(\x | \d)
\end{align}
which is the expected value of the entropy of the posterior, averaged over
all possible datasets which might be observed.
This is difficult to compute because the expression
for the posterior distribution
\begin{align}
p(\x | \d) &= \frac{p(\x)p(\d | \x)}{p(\d)}
\end{align}
contains the marginal likelihood $p(\d)$.

@@

The signal has the form
\begin{align}
y(t) &= A \sin \left(\frac{2\pi t}{T} + \phi\right)
\end{align}
where $A$ is the amplitude, $T$ is the period, and $\phi$ is the phase.
I assumed the following priors:
\begin{align}
\log_e{A}   &\sim \textnormal{Normal}\left(0, 0.1^2\right)  \\
\log_{10} T &\sim \textnormal{Uniform}(-1, 0)  \\
\phi        &\sim \textnormal{Uniform}(0, 2\pi)
\end{align}
and the following conditional prior for the data:
\begin{align}
d_i | A, T, \phi &\sim \textnormal{Normal}\left(y(t_i), 0.1^2\right).
\end{align}
That is, the data is just the signal $y(t)$ observed at particular times
$\{t_1, ..., t_n\}$, with gaussian noise of standard deviation 0.1.

$A$ and $\phi$ are nuisance parameters. Let $\x = \log_{10} T$.
The prior standard deviation of the noise, $\sigma$, was set to 0.1.
These results were computed using a tolerance of 0.001 for every quantity.
Results:
